---
title: "Additional analyses"
author: "Joe Marlo"
date: "11/30/2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(lubridate)
library(magrittr)
library(boot)

tDataEx2 <- readRDS('Data/data_ex2_20170101-20170110.rds')
tDataEx3 <- readRDS('Data/data_ex3_20170704-20170710.rds')
tDataEx4 <- readRDS('Data/data_ex4_20170711-20170713.rds')

```

## Additional analyses of the same data


# Comparative analysis for control group, harmful group, and helpful group. (balance check)

```{r}
# rows by country
tDataEx3 %>%
  group_by(eGroup, eCountry) %>%
  summarize(n = n()) %>%
  ggplot(aes(x = reorder(eCountry, n), y = n)) +
  geom_col() +
  facet_wrap(~eGroup) +
  labs(x = "Country",
       y = "Number of queries")

# rows by language
tDataEx3 %>%
  group_by(eGroup, eLanguage) %>%
  summarize(n = n()) %>%
    ggplot(aes(x = reorder(eLanguage, n), y = n)) +
  geom_col() +
  facet_wrap(~eGroup) +
  labs(x = "Language",
       y = "Number of queries")

# rows by query
tDataEx3 %>%
  group_by(eGroup, eQ) %>%
  summarize(n = n()) %>%
  ggplot(aes(x = reorder(eQ, n), y = n)) +
  geom_col() +
  facet_wrap(~eGroup) +
  labs(x = "Query",
       y = "Number of queries")
  
```


# What is the percentage that a box has shown up with/without a helpline under three categories(control, helpful, harmful)?  In data (ex_3) 

```{r}
tDataEx3 %>%
  group_by(eGroup, bResultsReached) %>%
  summarize(Percent_shown = sum(bHelplineShown) / n()) %>%
  ggplot(aes(x = bResultsReached, y = Percent_shown)) +
  geom_col() +
  facet_wrap(~eGroup) +
  labs(title = "Percent suicide prevention box is shown per search group",
       x = "Box was shown",
       y = "Percent of time helpline was shown") +
  theme_minimal()

# which rows don't have the box but do have the helpline
View(tDataEx3[!(tDataEx3$bResultsReached) & tDataEx3$bHelplineShown,])

# ggsave(filename = "Plots/Rate_per_group.svg",
#        plot = last_plot(),
#        device = "svg",
#        width = 7,
#        height = 5)

tDataEx3 %>%
  group_by(eCountry, eGroup, bResultsReached) %>%
  summarize(Percent_shown = sum(bHelplineShown) / n()) %>%
  ggplot(aes(x = bResultsReached, y = Percent_shown)) +
  geom_col() +
  facet_grid(eCountry~eGroup) +
  labs(title = "Percent suicide prevention box is shown per search group and country",
       x = "Box was shown",
       y = "Percent of time helpline was shown")
```

### Correlation Plot
## What are the correlations between the variables in Study 2?

Below is a correlation matrix image for the variables in Study 2. 

# First, I dummy coded whether the SPR box popped up during the query, the language used, the country the IP address was in, and the type of phrase in the search (harmful, helpful, and control). 

You can see there is a high coorelation between the countries and their common language. Notice the red boxes. These are not relevant for analysis.

Next, you will notice there is a row near the bottom with several pink boxes. That row represents when the SPR box popped up. The pattern communicates that there is a high correlation between the SPR box popping up in the countries of the United Kingdom, the USA, Ireland, and Australia. There is not a significant correlation with the other countries. We notice the pattern that those are all countries where the primary language is English.

There is also a high correlation between the SPR box popping up with the harmful phrase searches. Notice the pink box on the bottom right. 

The correlation is significant for each of those combinations. . 

```{r}
library(fastDummies)
library(GGally)
study2dummyRef <- dummy_cols(tDataEx3, select_columns = c("bHelplineShown", "eLanguage", "eCountry", "eGroup"), remove_first_dummy = TRUE)
ggcorr(study2dummyRef, hjust = 0.75, size = 1.5)
```

### Harmful SPR Plot by Country and Language
## What is the difference between SPR pop-ups when a person makes a harmful Google search in various countries and their primary language?

Below are two bar plots of the harmful Google queries in Study 2. The harmful Google queries are divided by country.

As you can see, harmful Google queries were routed to the SPR box much more often when they were searched for in English, except in Canada. Harmful Google queries in other countries, whose primary languages are not English, were much less likely to be routed to the SPR box. 

```{r}
library(dplyr)
library(ggplot2)

study2harmful <- data.frame(tDataEx3[which(tDataEx3$eGroup=="harmful"),])
agg <- count(study2harmful, eLanguage, eCountry, bHelplineShown)
ecols <- c(English="darkgoldenrod1", Portuguese="dodgerblue4", Mandarin="midnightblue", Hindi="deepskyblue3", German="lightskyblue1", Japanese="green4",Korean="yellowgreen")
agg_ord <- mutate(agg,
                  bHelplineShown = reorder(bHelplineShown, -n, sum))
p1 <- ggplot(agg_ord) +
      geom_col(aes(x = eCountry, y = n, fill = eLanguage), position = "dodge") +
      scale_fill_manual(values = ecols)
p1 + facet_wrap(~ bHelplineShown) +
    labs(title = "Number of Harmful Google Queries Routed to Suicide Prevention Box",
       x = "Country Name & Queary Search Language",
       y = "Number of Harmful Queries") + 
       theme(plot.title = element_text(hjust = 0.5))
```


### Linear Model Coefficient
##

This still needs to be cleaned up a lot!

```{r}
library(sjPlot)
# This seems like the best model to fit the data. I removed all the variables from the plot that had high p-values
SPRlm <- lm(bHelplineShown ~ eCountry*eGroup, data = tDataEx3)
plot_model(SPRlm, sort.est=TRUE, rm.terms = c("eCountry [Ireland]", "eCountry [UK]", "eGroup [helpful]","eCountry [India]", "eGroup [harmful]", "eCountry [Japan]", "eCountry [Germany]", "eCountry [South Korea]", "eCountry[Australia]", "eCountry [Canada]", "eCountry [Brazil]", "eCountry [USA]", "eCountry [Australia]", "eCountryCanada:eGrouphelpful", "eCountryCanada:eGroupharmful", "eCountryBrazil:eGrouphelpful", "eCountryJapan:eGrouphelpful", "eCountryIndia:eGrouphelpful", "eCountrySouth Korea:eGrouphelpful"), show.values = TRUE, value.offset = .35, value.size=3, title = "Forest Plot of Suicide Prevention Box Shown", axis.title = "lm regression coefficients", axis.labels = c("Germany * helpful", "India * harmful", "Germany * harmful", "Brazil * harmful", "South Korea * harmful", "Australia * helpful", "Ireland * helpful", "UK * helpful", "Japan * harmful", "USA * helpful", "Ireland * harmful", "USA * harmful", "UK * harmful", "Australia * harmful"))

```


SPR display rate segmented per server and country
```{r}

tDataEx3 %>%
  group_by(eServer, eCountry) %>%
  summarize(Percent_shown = sum(bHelplineShown) / n()) %>%
  ggplot(aes(x = eServer, y = Percent_shown)) +
  geom_col() +
  facet_wrap(~reorder(eCountry, Percent_shown)) +
  labs(title = "Percent of time SPR is shown segmented by country and server",
       x = "Server",
       y = "Percent of time SPR is shown")

```

SPR display rate by time and day of week
```{r}
tDataEx3 %>%
  # mutate(time = format(as.POSIXct(strptime(dCreate,"%Y-%d-%m %H:%M:%S",tz="")) ,format = "%H:%M")) %>%
  mutate(Hour = hour(dCreate)) %>%
  group_by(Hour, eCountry) %>%
  summarize(Percent_shown = sum(bHelplineShown) / n()) %>%
  ggplot(aes(x = Hour, y = Percent_shown, group = eCountry)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Percent of time SPR is show by hour of the day",
       x = "Hour of the day",
       y = "Percent of time SPR is shown")

tDataEx3 %>%
  # mutate(time = format(as.POSIXct(strptime(dCreate,"%Y-%d-%m %H:%M:%S",tz="")) ,format = "%H:%M")) %>%
  mutate(WeekDay = wday(dCreate)) %>%
  group_by(WeekDay, eCountry) %>%
  summarize(Percent_shown = sum(bHelplineShown) / n()) %>%
  ggplot(aes(x = WeekDay, y = Percent_shown, group = eCountry)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(limits = c(0, 1)) +
  labs(title = "Percent of time SPR is show by day of the week",
       x = "Day of the week",
       y = "Percent of time SPR is shown")
```


```{r original script, eval=FALSE, include=FALSE}

# function to bootstrap-calc 95% CI and return as data frame (ready for dplyr)
fCalcBootstrapCI <- function(.tData) {
  b <- boot(.tData, function(.tDataSub, .i) sum(.tDataSub$bHelplineShown[.i])/sum(.tDataSub$bResultsReached[.i]), 1000)
  ci <- boot.ci(b, type='perc')
  return(data.frame(
    n = sum(.tData$bResultsReached),
    helpline = 100*sum(.tData$bHelplineShown)/sum(.tData$bResultsReached),
    ci_l = 100*ci$percent[4],
    ci_u = 100*ci$percent[5]
  ))
}


# study 1: comparison between Germany and the US
tDataEx2 %>% 
  group_by(eLocation) %>%
  summarise(n=n())

tDataEx2 %>%
  mutate(Group=factor(eType,
                      levels=c('helpful', 'harmful', 'unrelated'),
                      labels=c('helpful', 'harmful', 'unrelated'))) %>%
  group_by(eLocation, dDay, Group) %>%
  do(fCalcBootstrapCI(.)) %>%
  ggplot(aes(dDay, helpline, group=Group, linetype=Group, shape=Group, fill=Group, color=Group)) +
  geom_ribbon(aes(ymin=ci_l, ymax=ci_u), fill='grey90', color=NA) +
  geom_line(size=.7) +
  geom_point(size=3.3) +
  facet_grid(eLocation ~ .) +
  scale_x_date(date_labels='%m/%d', date_breaks='1 day', name=' \nDate') +
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, 10), name='Share of results displaying the suicide prevention result [%]\n ') +
  theme_bw() +
  theme(legend.position = 'bottom') +
  scale_colour_brewer(palette='Paired')
ggsave('ex2_percentage-over-time_countrywise.png', device='png', width=10)

# study 2: comparison across the globe (main language only)
tDataEx3 %>% nrow
tDataEx3 %>%
  group_by(dDay = as.Date(dCreate), eGroup) %>%
  do(fCalcBootstrapCI(.)) %>%
  ggplot(aes(dDay, helpline, color=eGroup)) +
    geom_line() +
    geom_point() +
    geom_ribbon(aes(ymin=ci_l, ymax=ci_u), alpha=.2, color=NA)

fCalcBootstrapCI(tDataEx3 %>% filter(eGroup == 'harmful'))
fCalcBootstrapCI(tDataEx3 %>% filter(eGroup == 'helpful'))

tDataEx3 %>%
  group_by(eCountry, eGroup) %>%
  do(fCalcBootstrapCI(.)) %>%
  arrange(eGroup, desc(relative)) %>%
  View

tDataEx3 %>%
  filter(eGroup != 'control') %>%
  group_by(eCountry, eGroup) %>%
  do(fCalcBootstrapCI(.)) %>%
  mutate(
    Group = factor(eGroup, 
                   levels=c('helpful', 'harmful'),
                   labels=c('helpful', 'harmful')),
    Country = factor(eCountry,
                     levels=c('China', 'Canada', 'India', 'South Korea', 'Brazil', 'Germany', 'Japan', 'USA', 'UK', 'Australia', 'Ireland'),
                     labels=c('Singapore\n(Mandarin)', 'Canada\n(English)', 'India\n(Hindi)', 'South Korea\n(Korean)', 'Brazil\n(Portuguese)', 'Germany\n(German)', 'Japan\n(Japanese)', 'USA\n(English)', 'UK\n(English)', 'Australia\n(English)', 'Ireland\n(English)'))
  ) %>%
  ggplot(aes(Country, helpline, fill=Group)) +
    geom_bar(stat='identity', position=position_dodge(), width=.80) + #geom_bar doppelt, um Reihenfolge festzusetzen
    geom_tile(aes(x='Ireland\n(English)',    y=11/2,   width=.98, height=11, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Australia\n(English)',  y=10.6/2, width=.98, height=10.6, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='UK\n(English)',         y=6.2/2,  width=.98, height=6.2, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='USA\n(English)',        y=12.1/2, width=.98, height=12.1, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Japan\n(Japanese)',     y=18.5/2, width=.98, height=18.5, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Germany\n(German)',     y=9.2/2,  width=.98, height=9.2, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Brazil\n(Portuguese)',  y=5.8/2,  width=.98, height=5.8, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='South Korea\n(Korean)', y=28.9/2, width=.98, height=28.9, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='India\n(Hindi)',        y=21.1/2, width=.98, height=21.1, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Canada\n(English)',     y=9.8/2,  width=.98, height=9.8, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_tile(aes(x='Singapore\n(Mandarin)', y=7.4/2,  width=.98, height=7.4, fill='suicide rate per 100,000 inhabitants'), inherit.aes=F, show.legend=T) +
    geom_bar(stat='identity', position=position_dodge(), width=.80) +
    geom_errorbar(aes(ymin=ci_l, ymax=ci_u), width=.5, position=position_dodge(.9)) +
    scale_x_discrete() +
    scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, 10), name=' \nShare of results displaying the suicide prevention result [%]') +
    coord_flip() +
    theme_bw() +
    theme(legend.position = 'bottom') +
    #scale_fill_brewer(palette='Paired')
    scale_fill_manual(values=c('#1f78b4', '#a6cee3', 'grey80'))
  
ggsave('ex3_percentage-per-country-and-group.png', device='png', width=10)
  


# study 3: comparison within multi-lingual country (india, china)
tDataEx4 %>% nrow
tDataEx4 %>%
  group_by(eCountry, eLanguage, eGroup) %>%
  do(fCalcBootstrapCI(.)) %>%
  View

tDataEx4 %>%
  mutate(
    dDay = as.Date(dCreate),
    eCountry = factor(eCountry,
                      levels=c('China', 'India'),
                      labels=c('Singapore', 'India'))) %>%
  group_by(eCountry, eLanguage, eGroup, dDay) %>%
  do(fCalcBootstrapCI(.)) %>%
  mutate(
    Language = eLanguage,
    Group = factor(eGroup, 
                   levels=c('harmful', 'helpful', 'control'),
                   labels=c('harmful', 'helpful', 'unrelated'))
  ) %>%
  ggplot(aes(dDay, helpline, group=Language, linetype=Language, shape=Language, fill=Language, color=Language)) +
    geom_ribbon(aes(ymin=ci_l, ymax=ci_u), fill='grey90', color=NA) +
    geom_line(size=.7) +
    geom_point(size=3.3) +
    facet_grid(eCountry ~ Group) +
    scale_x_date(date_labels='%m/%d', date_breaks='1 day', name='Date') +
    scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, 10), name='Share of results displaying the suicide prevention result [%]\n ') +
    theme_bw() +
    theme(legend.position = 'bottom') +
    scale_colour_brewer(palette='Paired')
ggsave('ex4_percentage-over-time_languagewise.png', device='png', width=10)
```



##Contrast model：use English as reference group (extra)
```{r}
#install.packages("lsmeans")
library(lsmeans)
data <- tDataEx4
res1 <- lm(bHelplineShown~factor(eLanguage), data=data)
language.est = lsmeans(res1, "eLanguage")
#use English as reference group
Contrasts.English.ref = list(Mandarin.vs.English = c(1, -1, 0, 0), Hindi.vs.English = c(1, 0, -1,0), Telugu.vs.English = c(1, 0, 0, -1))
Test1 = contrast(language.est, Contrasts.English.ref)
test(Test1)
```


##Contrast model：compare each group to overall mean
```{r}
#compare each group to overall mean
Contrasts.group.averageref = list(English.vs.average = c(3/4, -1/4,-1/4,-1/4), Mandarin.vs.average = c(-1/4, 3/4,-1/4,-1/4), Hindi.vs.average = c(-1/4, -1/4,3/4,-1/4), Telugu.vs.average = c(-1/4, -1/4,-1/4, 3/4))
Test2 = contrast(language.est, Contrasts.group.averageref)
test(Test2)
```